---
title: "Fourth Amendment Decision-Making and Pregnancy Loss"
author: "Emma Marshall, JD, MA"
subtitle: "Comps Proposal"
format: 
  revealjs:
    theme: moon
    slide-number: true
    code-fold: true
---

# Overview {background-color="#1A936F"}

Descriptive statistics provide a summary that quantitatively describes a sample of data.

# Introduction 
Map of US with new post-Dobbs abortion restrictions. Expands the scope of criminal liability for pregnancy loss. 
# The Problems

## Distinguishing between Lawful and Criminal Pregnancy Loss

# Literature Review

## Ambiguity and the Fourth Amendment

### Standards of Suspicion: probable cause and reasonable suspicion

## Hindsight bias and the Fourth Amendment

## Components and Inputs of Hindsight Bias

Hindsight Bias Theory
-   Tendency to overestimate in hindsight without acknowledgement 
-   Sense-making process (Pezzo, 2003)
-   Component theory 
Inevitability impressions (objective likelihood) 
Foreseeability impressions (subjective) 

::: notes
Courts insist that judges can ignore irrelevant outcome information and accurately assess supporting evidence and determine the ex ante probability of a successful search, but a large body of psychological research on the hindsight bias has demonstrated that people often overestimate the predictability of an outcome with the benefit of hindsight (Fischhoff, 1975; Hawkins & Hastie, 1990; Roese & Vohs, 2012). 
According to the sense-making model, hindsight bias results from biased causal reasoning processes (Pezzo, 2003)

When given outcome information, people try to make sense of what  happened and often reinterpret the events leading up to that outcome in a way that makes it appear more inevitable or foreseeable than it would have been beforehand (Yopchick & Kim, 2012). 

The purpose of this research was to examine the extent to which the sense-making model of hindsight bias explains the tendency for people to overestimate the probability of a successful search in hindsight compared to foresight. 

:::
## Theoretical Framework

## Timeline


```{r}
#| label: setup
#| echo: false
#| eval: true
#| message: false
library(tidyverse)
library(emojifont)
library(showtext)
library(reactable)
library(kableExtra)
font_add_google("Ubuntu", "Ubuntu")
showtext_auto()
set.seed(1234)
population_df = tibble(ID = 1:200, 
                       x = rep(1:20, times = 10),
                       y = rep(1:10, each = 20),
                       Value = rnorm(200, 250, 50))
sample_size = 10
sample_ids = sample(1:200, size = sample_size, replace = FALSE)
sample_df =  filter(population_df, ID %in% sample_ids)
```

## Population

**Population** refers to the entire group of individuals that we want to draw conclusions about. 

```{r}
#| label: pop-people
#| eval: true
#| echo: false
#| fig-align: center
#| fig-height: 4.16
ggplot() +
  geom_text(data = population_df,
            mapping = aes(x = x,
                          y = y,
                          label = fontawesome('fa-user'),
                          colour = Value),
            family='fontawesome-webfont', size = 10) +
  scale_colour_gradient(low = "#F5CCCC", high = "#D00000") +
  labs(title = "Population: 200 people") +
  theme_void() +
  theme(legend.position = "none", 
        legend.title = element_blank(),
        plot.margin = margin(10, 10, 10, 10), 
        plot.title = element_text(face = "bold",
                                  hjust = 0.5,
                                  family = "Ubuntu",
                                  size = 36,
                                  margin = margin(b = 10)))

```

## Sample

**Sample** refers to the (usually smaller) group of people for which we have collected data on.

```{r}
#| label: samp-people
#| eval: true
#| echo: false
#| fig-align: center
#| fig-height: 4.16
ggplot() +
  geom_text(data = population_df,
            mapping = aes(x = x,
                          y = y,
                          label = fontawesome('fa-user')),
            family='fontawesome-webfont', size = 10, colour = "grey") +
  geom_text(data = sample_df,
            mapping = aes(x = x,
                          y = y,
                          label = fontawesome('fa-user'),
                          colour = Value),
            family='fontawesome-webfont', size = 10) +
  scale_colour_gradient(low = "#F5CCCC", high = "#D00000") +
  labs(title = glue::glue("Sample: {sample_size} people")) +
  theme_void() +
  theme(legend.position = "none", 
        legend.title = element_blank(),
        plot.margin = margin(10, 10, 10, 10), 
        plot.title = element_text(face = "bold",
                                  hjust = 0.5,
                                  family = "Ubuntu",
                                  size = 36,
                                  margin = margin(b = 10)))

```


## Hindsight Bias: Component View


```{mermaid}
flowchart LR
  A{Outcome} --> B1(Cognitive)
  A{Outcome} --> B2(Metacognitive)
  A{Outcome} -->B3(Motivational)
  B1(Cognitive) -- Knowledge updating --> C1(Memory Distortion)
  B1(Cognitive) -- Sense-making --> C2(Inevitability)
  B2(Metacognitive) -- Sense-fluency --> C3(Foreseeability fa:fa-camera-retro)
  B3(Motivational) -- Self-relevance --> C3(Foreseeability fa:fa-camera-retro)
  C2(Inevitability) --> D1(Overconfidence)
  C2(Inevitability) --> D2(Myopia)
  C3(Foreseeability) --> D2(Myopia)
```

